---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# Intuitionistic Fuzzy Inference Systems 🤖

<!-- badges: start -->
<!-- badges: end -->

The **rinfis** package aims to create user-friendly functions about intuitionistic fuzzy inference systems and thus support the works in this field.

## Installation

You can access the package using the codes below;

```{r eval=FALSE, include=T}
install.packages("devtools")
devtools::install_github("busenurk/rinfis")
```


## References

- Chaira, T. (2011) A novel intuitionistic fuzzy C means clustering algorithm and its application
to medical images, _Applied Soft Computing_, Vol. 11(2), 1711-1717. [📃](https://www.sciencedirect.com/science/article/pii/S1568494610001067)

- Chaira, T., Ray, A. K., Salvetti, O. (2006) Intuitionistic fuzzy C means clustering in medical images, _Advances in Pattern Recognition_, 226-230. [📃](https://www.worldscientific.com/doi/10.1142/9789812772381_0037)

- Bezdek, J. C., Hall, L.A., Clark, L.P. (1993) Review of MR segmentation technique in pattern recognition, Medical Physics Vol. 10 (20), 33-48.
[📃](https://pubmed.ncbi.nlm.nih.gov/8413011/)


